\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-04-30 project-writings/paper.tex
Cite type inference paper

In IonMonkey, Mozilla's next-generation optimizing Javascript JIT
compiler, an approximate type inference system is used to generate
type-specialized code for the common case of integer arithmetic, and
type guards are inserted if the type inferencer is not certain. The
catch is that since double precision floats have a larger range than
32-bit integers, if the integer operations would overflow the result
must be promoted to being stored in a double. IonMonkey deals with
this by inserting overflow checks after arithmetic operations and
bailing out of the type specialized code if they trip. While this is
sometimes actually necessary, it is frequently the case that overflow
is not possible.

>>>>

In IonMonkey, Mozilla's next-generation optimizing Javascript JIT
compiler, a hybrid type inference system (which uses both static analysis and
runtime information\cite{BHackettTI}) is used to generate
type-specialized code for the common case of integer arithmetic, and
type guards are inserted if the type inferencer is not certain. The
catch is that since double precision floats have a larger range than
32-bit integers, if the integer operations would overflow the result
must be promoted to being stored in a double. IonMonkey deals with
this by inserting overflow checks after arithmetic operations and
bailing out of the type specialized code if they trip. While this is
sometimes actually necessary, it is frequently the case that overflow
is not possible.
